Response to the defense feedback

### 2021-06-01 Chapter-5/Chapter-5.tex
Updates from Overleaf

\subsection{Channel Capacity}
$K$ is a random variable.
Let $k$ be one of the possible
values of $K$. The Shannon entropy $H(K)$ is defined as
\begin{equation}\label{chapter5:eq1}
  H(K) = - \sum_{k {\in} K}p(k)\log_2(p(k))
\end{equation}

@@

In this chapter, we use the channel capacity to describe the amount of information leakages through a channel. In information theory, the channel capacity is used to quantify the rate of information can be reliably transmitted over a channel. If we use $K$ to represent the input secrets and $O$ to represent the output observation. The channel capacity ($C$) is defined as

@@

Table~\ref{chapter5:table:over_result} presents the overview result. The minimum unit of the program during the experiment is the function. Suppose the function has more than one access map, then the function that is vulnerable to side-channel attacks. We measure the side-channel leakages at two different granularities: the byte level and the cache line level. The result shows that the program has more leaked vulnerabilities and tends to leak more information at the byte level than the cache line level. Each time we run the target program under random inputs and record memory accesses. For cryptography programs, we run the target program with $4096$ different inputs. During the fuzzing process, if the program does not have a new memory access bitmap after several rounds. We call the fuzzing step is fixed. From the side-channel detection aspect, it is not necessary to continue running the experiments since more rounds do not reveal new leakages. During the experiment, we find AES ciphers reach the fixed point after about 300 rounds, and RSA can reach the fixed point after around 500 rounds. Previous work~\cite{weiser2018data} also reported a similar result. We continue running the experiment during our experiment until the observed value for the same observation is at least 5 to satisfy the Chi-square test requirement. Therefore, we choose to run all the cipher with different inputs for $4096$ times.  If one program has more than two leaked functions, we run the chi-squared test and calculate the total amount of leakages.

>>>>

\subsection{Channel Capacity}
Given a discrete random variable $K$,
$k$ is one of the possible
values occurring with the probability $p(k)$. The Shannon entropy $H(K)$ is defined as
\begin{equation}\label{chapter5:eq1}
  H(K) = - \sum_{k {\in} K}p(k)\log_2p(k)
\end{equation}

@@

For a deterministic program, the program should always have the same memory access patterns under the same input. Therefore, an address-based side-channel attack can be seen as a communication channel between the memory access patterns and secret inputs. In this chapter, we use the channel capacity to describe the amount of information leakages through a channel. In information theory, the channel capacity is used to quantify the rate of information can be reliably transmitted over a channel. If we use $K$ to represent the input secrets and $O$ to represent the output observation. The channel capacity ($C$) is defined as

@@

Table~\ref{chapter5:table:over_result} presents the overview result. The minimum unit of the program during the experiment is the function. Suppose the function has more than one access map, then the function that is vulnerable to side-channel attacks. We measure the side-channel leakages at two different granularities: the byte level and the cache line level. The result shows that the program has more leaked vulnerabilities and tends to leak more information at the byte level than the cache line level. Each time we run the target program under random inputs and record memory accesses. For cryptography programs, we run the target program with $4096$ different inputs. During the fuzzing process, if the program does not have a new memory access bitmap after several rounds. We call the fuzzing step is fixed. From the side-channel detection aspect, it is not necessary to continue running the experiments since more rounds do not reveal new leakages. During the experiment, we find AES ciphers reach the fixed point after about 300 rounds, and RSA can reach the fixed point after around 500 rounds. Previous work~\cite{217537} also reported a similar result. We continue running the experiment during our experiment until the observed value for the same observation is at least 5 to satisfy the Chi-square test requirement. Therefore, we choose to run all the cipher with different inputs for $4096$ times.  If one program has more than two leaked functions, we run the chi-squared test and calculate the total amount of leakages.
